### 2012-12-04 inst/examples/policycosts/figure4.Rmd
farm fast figure4
index by npv0 fraction (fixes typo)

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

>>>>

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
index by npv0 fraction (fixes typo)

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1 * c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

@@

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

@@

>>>>

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

@@

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

```{r}
save(list=ls(), file="policycosts.rda")
```

@@

Calculate statistics of variance and autocorrelation for Figure 4.

```{r}
v <- dt[,var(harvest), by=penalty_fn]
a <- dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
v
a
```
